\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{xcolor}

\usepackage{tikz}
\usepackage{lipsum}
\usepackage{multicol}

% Define custom colors
\definecolor{darkblue}{HTML}{16417C}
\definecolor{lightblue}{HTML}{46A9F7}

% change color hyperlinks
\hypersetup{%
    colorlinks=true,% hyperlinks will be black
    urlcolor=[rgb]{0.04,0,0.5},
    urlbordercolor=[rgb]{0.7,0.7,0.7},% hyperlink borders will be gray
    pdfborderstyle={/S/U/W 0.5}% border style will be underline of width 1pt
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}
{\centering\bfseries\color{darkblue}\fontsize{14}{18}\selectfont}
{}{0em}{}
[\color{darkblue}\vspace{-12pt}\titlerule\vspace{-12pt}]

%-------------------------
% Custom commands
\renewcommand{\titlerule}{\rule{\textwidth}{2pt}}

\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{#2 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemPaper}[1]{
    \item\small{
            {#1}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \color{lightblue}\textbf{#1} & #2 \\
        \textbf{\textit{\small#3}} & \textit{\small #4} \\
        \textnormal{}\vspace{-5pt}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]\setlength\itemsep{0em}\vspace{-1pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
    %----------HEADING-----------------
    \begin{tikzpicture}[remember picture,overlay]

        \coordinate [below=80pt] (midpoint) at (current page.north);
        
        \node [
        name = colourbar,
        anchor = south,
        fill = lightblue!60,
        text = white,
        minimum width=\paperwidth,
        minimum height=80pt] at (midpoint) {
            \begin{tabular}{c}
                \\
                \\
                \textbf{\Large Amri Rasyidi} \\
                \href{mailto:amri.geodesy@gmail.com}{amri.geodesy@gmail.com} \\ 
                \href{https://www.linkedin.com/in/amri-rasyidi/}{\fontsize{14}{20}\faLinkedin ~Amri Rasyidi}
                \href{https://github.com/amrirasyidi}{\fontsize{14}{20}\faGithub ~amrirasyidi}
                \href{https://arasyidi.netlify.app/}{\fontsize{14}{20}\faGlobe ~arasyidi.netlify.app}
            \end{tabular}
        };
    \end{tikzpicture}
    
    \vspace{20pt}
    \section{Summary}
    {Bachelor of Science in Geodesy and Geomatics Engineering with a strong passion for 
    spatial science and data science. Over 5 years of experience in the data industry, 
    including 2 years dedicated to data science. Shows Commitment to continuous learning and 
    growth, by maintain a blog documenting my data science journey and insights into 
    life. Possess leadership experience and actively volunteer to teach data science to 
    others, demonstrating a commitment to knowledge sharing and community engagement.}
    \vspace{-5pt}
    %--------SKILLS------------
    \section{Skills and Stack}
    % \begin{multicols}{3} % Set the number of columns to 3
    %     \resumeItemListStart
    %         \resumeItemPaper{Machine Learning, Deep Learning, MLOps}
    %         \resumeItemPaper{PyTorch}
    %         \resumeItemPaper{scikit-learn}
    %         \resumeItemPaper{XGBoost}
    %         \resumeItemPaper{statsmodel}
    %         \resumeItemPaper{MLFlow}
    %         \resumeItemPaper{Optuna}
    %         \resumeItemPaper{Data Science}
    %         \resumeItemPaper{VSCode}
    %         \resumeItemPaper{GeoPandas}
    %         \resumeItemPaper{Apache-Sedona}
    %         \resumeItemPaper{polars}
    %         \resumeItemPaper{ydata-profiling}
    %         \resumeItemPaper{SQL}
    %     \resumeItemListEnd
    % \end{multicols}
    % \vspace{-15pt}
    \resumeItemListStart
    \resumeItem{Machine Learning, Deep Learning, MLOps:}{ % 8bd274, C8cfd4
        PyTorch, , XGBoost, MLFlow, Optuna, 
        \textcolor[HTML]{8bd274}{scikit-learn, statsmodel},
        \textcolor[HTML]{C8cfd4}{TensorFlow, Darts, DVC}
    }
    \resumeItem{Data Science:}{
        VSCode, GeoPandas, Apache-Sedona, polars, ydata-profiling, BigQuery SQL, ArcGIS Pro
        \textcolor[HTML]{C8cfd4}{Neo4j, Cypher}, 
    }
    \resumeItem{Deployment:}{
        Git, GitHub, DagsHub, 
        \textcolor[HTML]{8bd274}{Gradio},
        \textcolor[HTML]{C8cfd4}{HuggingFace, Azure, AWS}
    }
    \resumeItem{Relevant coursework:}{
        graph data science,
        spatial analysis,
        time series forecasting,
        clustering,
        classification
    }
    % \resumeItem{Technical:}{
    %     Data Science Python,
    %     ArcGIS,
    %     SQL (BigQuery), 
    %     Deep Learning (PyTorch),
    %     Tableau,
    %     Git,
    %     % \LaTeX.
    % }
    % \resumeItem{Relevant coursework:}{
    %     data science,
    %     machine learning,
    %     deep learning,
    %     forecasting,
    %     clustering,
    %     classification,
    %     data analytic,
    %     spatial analysis
    % }
    \resumeItem{Languages:}{
        Bahasa Indonesia (Native), 
        English (CEFR Level C1/IELTS 7.5).
    }
    % \resumeItem{Summary:}{
    %     x
    % }
    \resumeItemListEnd
    
    %-----------PRO EXPERIENCE-----------------
    \vspace{-5pt}
    \section{Professional Experiences}
    % \resumeSubHeadingListStart
    \resumeSubheading
    {ESRI Indonesia (GIS Software \& Services)}{Jakarta, Indonesia}
    {Data Scientist}{January 2023 – present}
    {Esri Indonesia provides GIS solutions and services to various industries in 
    Indonesia, including local and national government, natural resources, utilities, 
    transportation, telecommunications, and commercial.}
    \vspace{-5pt}
    \resumeItemListStart
    \resumeItem{GIS-Based Market Development:}{ collaborated with solution team to 
    developed a dashboard able to showcase current market presence and potential leads. 
    Handled the data processing pipeline capable of handling 193 million records, 
    reducing manual process time by 72\%. Applied a statistical method to classify 
    $\sim$300 top priority leads out of 4000 prospects
    }
    \resumeItem{GIS-Based Market Development:}{ created 2 custom geoprocessing tools to 
    handle spatio-temporal data processing capable of handling 193 million records.
    }
    \resumeItem{Air Quality Index (AQI) Forecasting:}{ developed a deep learning 
    timeseries forecasting pipeline to forecast the next 48 hours of AQI trends. 
    Designed 36 experimentation combination and used MLflow and Dagshub to monitor the 
    result. Best model achieve RMSE of $\sim$7.14
    }
    \resumeItemListEnd
    
    \vspace{5pt}
    \resumeSubheading
    {Zenius Education (Ed-Tech)}
    {Jakarta, Indonesia}
    {Business Intelligence Analyst}
    {December 2021 - July 2022}
    {Zenius is a well-know ed-tech company pioneer focus on increasing thinking 
    capacity and building foundational thinking for junior and senior high school 
    student to help them excel in their school}
    \vspace{-5pt}
    \resumeItemListStart
    \resumeItem{Workflow management:}{ \textit{structured a system to increase 
    workflow transparency and accountability}. Increased the ability to manage 
    and monitor ad hoc and internal tasks/projects \textcolor{blue}{from 0 to 
    16+ tasks/projects weekly}.}
    \resumeItem{Dashboard:}{ created \textcolor{blue}{3 dashboards} with 
    \textcolor{red}{google data studio} for \textcolor{green}{growth, finance, 
    and content teams} with over \textcolor{blue}{50 metrics} ranged from 
    operational to C-level granularity.}
    \resumeItemListEnd

    \vspace{5pt}
    \resumeSubheading
    {Gojek (Q-commerce and Financial Services)}
    {Jakarta, Indonesia}
    {Junior Risk Data Analyst $\Rightarrow$ Risk Data Analyst}
    {April 2019 - December 2021}
    {GoTo’s ecosystem comprises of on-demand transport, e-commerce, food and grocery 
    delivery, logistics and fulfillment, and financial services through the Gojek, 
    Tokopedia and GoTo Financial platforms.}
    \vspace{-5pt}
    \resumeItemListStart
    \resumeItem{Fraud analysis:}{ \textcolor{blue}{analyzed up to 1000 GPS movements} 
    \textcolor{yellow}{daily} to determine fraudulent patterns for constructing fraud 
    rules of fourwheels and two-wheels platforms.}
    \resumeItem{Rule deployment:}{ prevented new modus operandi from exploiting a GPS 
    related-loophole in the production apps. Fraudsters abused this loophole for 
    financial gain and reputation hijack. \textcolor{blue}{Reduced the number of
    case significantly from 400 to 10 cases daily, with false positive rate under 1\%} 
    \textcolor{yellow}{within a month}.}
    \resumeItem{Rule enhancement:}{ \textit{analyzed the hypothesis made fraud my 
    team then enhanced the rule by applying a more sophisticated method} of fraud 
    identification (relational graph logic) to detect the convoluted device 
    connection/relation. \textcolor{blue}{Increased the detection rate by 50\%}.}
    \resumeItemListEnd

    % \resumeSubHeadingListEnd

    %-----------PROJECT-----------------
    \vspace{-5pt}
    \section{Projects}

    \resumeItemListStart
    \resumeItem{Book Recommendation System:}{ built a local web app to give user a book recommendation based on collaborative filtering logic.
    Also created a simple search engine to ensure users are asking the correct book to be recommended. 
    \href{https://github.com/amrirasyidi/book_recommendation}{[\textcolor{blue}{repository}]}}
    \resumeItem{MIT IDSS Course - Hackaton:}{ the objective of this problem is to understand which parameters play an important role in swaying
    passenger feedback towards a positive scale. Created logistic regression, XGBoost, and Deep learning model resulting in accuracy
    above 92\%. 
    \href{https://github.com/amrirasyidi/mit_idss_hackaton}{[\textcolor{blue}{repository}]}}
    \resumeItem{JDVF - Tableau Dashboard:}{ this dashboard provides the government, NGO, and researcher among many other stakeholders a start
    to make data-driven decisions and policy-making regarding flood mitigation in West Java. 
    \href{https://public.tableau.com/app/profile/faisal.putra/viz/Book1_16671939458310/DashboardFINAL}{[\textcolor{blue}{Tableau Public}]}}
    \resumeItemListEnd
    
    %-----------Educations-----------------
    \vspace{-5pt}
    \section{Educations}

    \resumeSubheading
    {MIT IDSS: Data Science and Machine Learning}
    {Remote}
    {An online professional course taught by the MIT faculty}
    {August - November 2022}
    {Topic covered: statistics, unsupervised and supervised learning, hypothesis testing, 
    deep learning, recommendation system, network and graphical model, and predictive analysis.}
    
    \vspace{5pt}
    \resumeSubheading
    {Institut Teknologi Bandung}
    {Bandung, Indonesia}
    {B.Sc in Geodesy and Geomatics Engineering, GPA 3.21/4.00.}
    {July 2014 - October 2018}
    {Topic covered includes: calculus, statistics, GIS, satellite geodesy, 
    remote sensing, spatial database, cartography.}

    %-----------Leadership/Voluntary Experiences-----------------
    \vspace{-5pt}
    \section{Leadership/Voluntary Experiences}

    \resumeSubheading
    {Yayasan Anak Bangsa Bisa (YABB)}
    {Jakarta, Indonesia}
    {Mentor/Instructor - Generasi Gigih}
    {July - December 2021}
    {Yayasan Anak Bangsa Bisa (YABB) is a non-profit organization founded by Gojek, a catalyst that enables resilient change makers to
    solve pressing challenges and build sustainable communities. Generasi Gigih programme focuses on generating tech-talent by
    conducting intensive bootcamp to prepare fresh graduates for the tech industry.}
    \vspace{-5pt}
    \resumeItemListStart
    \resumeItem{Designed and created:}{ data analysis lecture materials (Python and SQL for data analysis).}
    \resumeItem{Gave Lecture:}{ on data analysis.}
    \resumeItem{Mentorship:}{ guide and mentor to the participants during their internship. Ensured the participants gained the most during their
    internship while maintaining the focus of the projects they were working.}
    \resumeItemListEnd

    \vspace{5pt}
    \resumeSubheading
    {Ikatan Mahasiswa Geodesi ITB (IMG-ITB)}
    {Bandung, Indonesia}
    {Chairman of IMG-ITB (Executive Student Council)}
    {August 2017 – March 2018}
    {Ikatan Mahasiswa Geodesi ITB (IMG-ITB) is a profession-based student association.}
    \vspace{-5pt}
    \resumeItemListStart
    \resumeItem{Visioning:}{ designed a blueprint as the north star metrics of the association. Mainly focus on character and mindset development in a
    professional manner and making concrete social impact.}
    \resumeItem{Executive function:}{ managed a council consisted of 5 ministries and 15 departments to maintain and develop the student association.}
    \resumeItemListEnd

    %-----------MISCELLANEOUS-----------------
    \vspace{-5pt}
    \section{Miscellaneous}

    \resumeItemListStart
    \resumeItem{Topic:}{ education, environment, game industry, movie, leisure.}
    \resumeItem{Book:}{ history, sociology, biography, religion, psychology.}
    \resumeItem{Activity:}{ SCUBA diving, hiking, gym, PC game, writing.}
    \resumeItemListEnd

\end{document}