\resumeSubheading
{ESRI Indonesia (GIS Software \& Services)}{Jakarta, Indonesia}
{Data Scientist}{January 2023 – present}
\small{Esri Indonesia provides GIS solutions and services to various industries in 
Indonesia, including local and national government, natural resources, utilities, 
transportation, telecommunications, and commercial.}
\vspace{-1pt}
\resumeItemListStart
\resumeItem{Road Damage Detection:}{ created a data engineering pipeline to convert $\sim$16k raw images and labels data from multiple sources to ready-to-train data. Trained a deep learning model using YOLOv8 and achieved a precision-recall score of 0.635 across all 4 classes.}
\resumeItem{GIS-Based Market Development:}{ collaborated with the solution team to 
develop a dashboard able to showcase current market presence and potential leads. 
Created a custom data processing pipeline capable of handling 193 million records, 
reducing manual process time by 72\%. Applied a statistical method to classify 
$\sim$300 top priority leads out of 4000 prospects
}
\resumeItem{PM2.5 Forecasting:}{ developed a deep learning time-series forecasting pipeline to forecast the next 48 hours of PM2.5 trends. Designed $>$80 experiment combinations and used MLflow and Dagshub to monitor the result. The best model achieved RMSE of $\sim$7.14.
}
\resumeItemListEnd

\vspace{5pt}

\resumeSubheading
{Zenius Education (Ed-Tech)}
{Jakarta, Indonesia}
{Business Intelligence Analyst}
{December 2021 - July 2022}
\small{Zenius is a well-known ed-tech company pioneer focused on increasing thinking 
capacity and building foundational thinking for junior and senior high school 
student to help them excel in their school.}
\vspace{-1pt}
\resumeItemListStart
\resumeItem{Workflow management:}{ structured a system to increase 
workflow transparency and accountability. Increased the ability to manage 
and monitor ad hoc and internal tasks/projects from 0 to 
16+ tasks/projects weekly.}
\resumeItem{Dashboard:}{ created 3 dashboards with Google Data Studio for growth, finance, and content teams with over 50 metrics ranging from operational to C-level granularity.}
\resumeItemListEnd

\vspace{5pt}

\resumeSubheading
{Gojek (Q-commerce and Financial Services)}
{Jakarta, Indonesia}
{Junior Risk Data Analyst $\Rightarrow$ Risk Data Analyst}
{April 2019 - December 2021}
\small{GoTo’s ecosystem comprises of on-demand transport, e-commerce, food, and grocery delivery, logistics and fulfillment, and financial services through the Gojek, Tokopedia and GoTo Financial platforms.}
\vspace{-1pt}
\resumeItemListStart
\resumeItem{Fraud analysis:}{ analyzed up to 1000 GPS movements
daily to determine fraudulent patterns for constructing fraud 
rules of fourwheels and two-wheel platforms.}
\resumeItem{Rule deployment:}{ prevented new modus operandi from exploiting a GPS 
related-loophole in the production apps. Fraudsters abused this loophole for 
financial gain and reputation hijack. Reduced the number of
case significantly from 400 to 10 cases daily, with a false positive rate under 1\%
within a month.}
\resumeItem{Rule enhancement:}{ analyzed the hypothesis made fraud my 
team then enhanced the rule by applying a more sophisticated method of fraud 
identification (relational graph logic) to detect the convoluted device 
connection/relation. Increased the detection rate by 50\%.}
\resumeItemListEnd
