\resumeSubheading
{Dealls}
{Remote}
{Mentor}
{July 2024 - Present}
\small{Dealls is Indonesia's leading job portal, offering high-quality job listings from over 3,500 top companies. It also provides free career development programs, including mentoring and CV review services, to help job seekers secure their dream careers more easily.}
\vspace{-1pt}
\resumeItemListStart
\resumeItem{Super Mentor:}{ guiding professionals in navigating their career in the data industry. Provides a free-of-service career consultation.}
\resumeItemListEnd

\vspace{5pt}
\resumeSubheading
{RevoU x MSIB}
{Remote}
{Mentor}
{February - April 2024}
\small{RevoU is Indonesia’s Largest Professional Skilling Platform. MSIB is a comprehensive career preparation program initiated by ministry of education and culture.}
\vspace{-1pt}
\resumeItemListStart
\resumeItem{Mentorship:}{ guiding students interested in pursuing careers as data analysts and data scientists. Conducted live sessions to provide technical skills, while also creating comprehensive learning materials to support their journey into the tech field.}
\resumeItemListEnd

\vspace{5pt}
\resumeSubheading
{Yayasan Anak Bangsa Bisa (YABB)}
{Jakarta, Indonesia}
{Mentor/Instructor - Generasi Gigih}
{July - December 2021}
\small{Yayasan Anak Bangsa Bisa (YABB) is a non-profit organization founded by Gojek, a
catalyst that enables resilient change makers to solve pressing challenges and build
sustainable communities. Generasi Gigih programme focuses on generating tech-talent
by conducting an intensive boot camp to prepare fresh graduates for the tech industry.}
\vspace{-1pt}
\resumeItemListStart
\resumeItem{Designed, created, and lectured:}{ data analysis lecture materials (Python and SQL
for data analysis).}
\resumeItem{Mentorship:}{ guide and mentor the participants during their internship. Ensured the participants gained the most during their internship while maintaining the focus on the projects they were working on.}
\resumeItemListEnd

\vspace{5pt}
\resumeSubheading
{Ikatan Mahasiswa Geodesi ITB (IMG-ITB)}
{Bandung, Indonesia}
{Chairman of IMG-ITB (Executive Student Council)}
{August 2017 – March 2018}
\small{Ikatan Mahasiswa Geodesi ITB (IMG-ITB) is a profession-based student association.}
\vspace{-1pt}
\resumeItemListStart
\resumeItem{Visioning:}{ designed a blueprint as the north star metrics of the
association. Mainly focus on character and mindset development in a
professional manner and making a concrete social impact.}
\resumeItem{Executive function:}{ managed a council consisting of 5 ministries and 15
departments to maintain and develop the student association.}
\resumeItemListEnd
